The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-10 paper/ms.tex
bedding corrections

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87Jd}. The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored. The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest. In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from objects in the same column. This is a particularly serious issue for faint objects in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.

One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star. This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.

Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants. \textcolor{red}{Get frequencies}.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.

@@

While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters as through these scaling relations:

@@

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} \left(\dfrac{R}{\rsun}\right)^{-3}}
\end{equation}

@@

To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

@@

Once \numax has been estimated, we have used the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.

For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element. This resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces). We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}. } 
\end{figure*}
The $\alpha$ elements are thought to form in  variety ways during internal fusion within a star while it evolves over its life. These elements are then largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. The most important of these diagrams are those including the abundances of the $\alpha$ elements as a function of metallicity. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{We note that there are likely systematics between our [X/Fe] abundance scale and those of our comparison samples. We do not have the relevant data, which include several stars in common with these studies but observed with the TRES spectrograph, to asses the level of systematics.}  to representative disk stars from \cite[open red square,][]{Bensby2014} and \cite[open orange triangles,][]{Adibekyan2012}.

@@

Red clump stars, which burn helium in their cores, differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence. They can therefore be distinguished from hydrogen-shell burning giants asteroseismologically, due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}. 
The moniker `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}. This property makes them useful standard candles to which distances can be accurately computed from photometry. Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}. \gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and in particular hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}. While precise characterization of these stars to the necessary degree is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.

@@

For all the main sequence stars in our sample, we visually inspected light curves and power spectra to determine their variability class. In the following subsections, we will briefly comment on some of the findings. As main sequence variables are so diverse, and suited to varied science cases, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also resembles that of an SPB star, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.

>>>>

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87J}. The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored. The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest. In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column. This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column. If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these stars as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.

The coolest main sequence star, BD+43~3068, is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue. It is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star. Its light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.

Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants. \textcolor{red}{Get frequencies}.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.

@@

Among the~64 red giants identified in this sample, for~30 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
\end{equation}

@@

To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

@@

Once \numax has been estimated, we have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra. Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.

For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu. One star in our sample, HD~185351, has a mode envelope that is not well fit by our model. The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ (a so-called `retired~A star') and used it to calibrate the convective overshoot parameter for low-luminosity red giants. The global asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.

@@

We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element. Although this resolution and SNR are sufficient for an exploratory study, for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750. % figure out this discrepancy?

@@

\subsubsection{Chemical Composition}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations to which these stars belong. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces). We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}. } 
\end{figure*}
The $\alpha$ elements are largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{There are likely to be systematics between our [X/Fe] abundance scale and those of our comparison samples.}  to representative disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

@@

Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \emph{g}-mode period spacings \citep{rggmodehelium}. 
The term `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}. This property makes them useful standard candles to which distances can be accurately computed from photometry. Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}. \gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and in particular hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).

From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}. While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.

@@

For all the main sequence stars in our sample, we inspected light curves and power spectra to determine their variability class. In the following subsections, we will briefly comment on some of the findings. Since main sequence variables are so diverse, and the relevant scientific questions so varied, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also resembles that of an SPB star, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

Another star with a hump-and-spike spectrum is Boyajian's~Star (KIC~8462852), which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
